
---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->



[![Travis Build Status](https://travis-ci.org/tidyverse/ggplot2.svg?branch=master)](https://travis-ci.org/tidyverse/ggplot2)


## Overview

touristR is a tourist friendly R package providing useful information to help fellow travellers find the best locations to visit worldwide.

## Installation

```{r, eval = FALSE}

#Please install the development version from GitHub:
#install.packages("devtools")
#devtools::install_github("AyrtonRua/group1_project")

```


## Usage

Please refer to the documentation of each function *run_shiny*,
*track_twitter_hashtag* and *getTopNAttractions*, for further information
on how to use each function.  

Nonetheless, please find bellow an example from each function:

```{r, eval = FALSE}

#run_shiny (interactive Shiny app)
#Choose a city = London
#relative sentiment? (check or not)

#track_twitter_hashtag
# track_keyword(
# keyword = c("eiffel tower", "san francisco", "london"),
# type="place"
# number = 2,
# sincetype = "weeks",
# provideN = 100
# )

#getTopNAttractions
# getTopNAttractions(
# city = "london",
# n = 10
# )

```



## Getting help

In case of any request including bugs, please open a new issue on the 
[GitHub repository of group 1](https://github.com/AyrtonRua/group1_project).



## References

Orso, S., Molinari, R., Lee, J., Guerrier, S., & Beckman, M. (2018). *An Introduction to Statistical Programming Methods with R*. Retrieved from https://smac-group.github.io/ds/



